<NAME> - an analyser framework for P4

### 2021-03-23 publications/The_tool_intro/paper.tex
tool_intro:adding authors and acks

	\author{}
	\email{}
	\orcid{}
	\author{}
	\authornotemark[]
	\email{}
	\affiliation{%
		\institution{}
		\streetaddress{}
		\city{}
		\state{}
		\country{}
		\postcode{}
	}

@@

	\keywords{TODO}

@@

>>>>

	\author{Dániel Lukács}
	\email{dlukács@inf.elte.hu}
	\orcid{0000-0001-9738-1134}
	\affiliation{%
		\institution{ELTE, Eötvös Loránd University, Faculty of Informatics}
        \country{Hungary}
        \city{Budapest}
	}

	\author{Gabriella Tóth}
	\email{kistoth@inf.elte.hu}
	\orcid{}
	\affiliation{%
		\institution{ELTE, Eötvös Loránd University, Faculty of Informatics}
        \country{Hungary}
        \city{Budapest}
	}

	\author{Máté Tejfel}
	\email{matej@inf.elte.hu}
	\orcid{0000-0001-8982-1398}
	\affiliation{%
		\institution{ELTE, Eötvös Loránd University, Faculty of Informatics}
        \country{Hungary}
        \city{Budapest}
	}

@@

	\keywords{P4 language, static analysis, analysis framework}

@@

\begin{acks}
The research has been supported by the European Union, co-financed by the European Social Fund 
(EFOP-3.6.3-VEKOP-16-2017-00002). M. Tejfel also thanks the support of the project
"Application Domain Specific Highly Reliable IT Solutions" implemented with the support of the NRDI Fund
of Hungary, financed under the Thematic Excellence Programme TKP2020-NKA-06 (National Challenges Subprogramme) funding scheme.
\end{acks}
